A Note on GMM Estimation of Theories of Expectation Formation

### 2019-10-24 notes/GMMResults.tex
1. Both NI and SE can do the loop estimation. Needs to do NI joint plots. 2. The notes include all figures except for NI joint. 3. Both Se and NI tables are included. But need to debug NI table.

\documentclass[]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[a4paper,bindingoffset=0.2in,%
left=1.2in,right=1.2in,top=1.2in,bottom=1.2in,%
footskip=.25in]{geometry}

%opening
\title{Note on GMM Estimation of Theories of Expectation Formation}
\author{Tao Wang}

@@

>>>>

\documentclass[]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[a4paper,bindingoffset=0.2in,%
left=0.9in,right=0.9in,top=1.2in,bottom=1.2in,%
footskip=.25in]{geometry}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage{tabularx}
\usepackage{rotating}

%opening
\title{A Note on GMM Estimation of Theories of Expectation Formation}
\author{Tao Wang}

@@

\subsubsection{Professional Forecasters}

Figure \ref{SE_diag_SPF} and \ref{SE_diag_joint_SPF} plot the estimated moments for SE model together with the data moments professional forecasts of SPF.

From left to the right, the four columns of the figures are based on estimation

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Estimation of SE for Professionals}
		\label{SE_diag_SPF}
		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag0.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag1.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag2.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag3.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_se_est_diag4.png}
	\end{subfigure}
	\vspace{1em}
	\vfill
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Joint Estimation of SE and Inflation Process}
		\label{SE_diag_joint_SPF}
	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag0.png}
	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag1.png}
	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag2.png}
	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag3.png}
	\includegraphics[width=0.19\textwidth]{figures/spf_se_est_joint_diag4.png}
	\end{subfigure}
	\\
	\begin{flushleft}
		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given. The bottom panel estimates the parameters of expectation formation and inflation process jointly. From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively. }
	\end{flushleft}
	\caption{SE of Professionals: Esimated Model Moments and Data Moments}
\end{figure}

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Estimation of NI for Professionals}
		\label{NI_diag_SPF}
		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag0.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag1.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag2.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag3.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_diag4.png}
	\end{subfigure}
	\vspace{1em}
	\vfill
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Joint Estimation of NI and Inflation Process}
		\label{NI_diag_joint_SPF}
		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag0.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag1.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag2.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag3.png}
		\includegraphics[width=0.19\textwidth]{figures/spf_ni_est_joint_diag4.png}
	\end{subfigure}
	\\
	\begin{flushleft}
		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given. The bottom panel estimates the parameters of expectation formation and inflation process jointly. From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively. }
	\end{flushleft}
	\caption{NI of Professionals: Esimated Model Moments and Data Moments}
\end{figure}

\subsubsection{Households}

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Estimation of SE for Households}
		\label{SE_diag_SCE}
		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag0.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag1.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag2.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag3.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_diag4.png}
	\end{subfigure}
	\vspace{1em}
	\vfill
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Joint Estimation of SE and Inflation Process}
		\label{SE_diag_joint_SCE}
		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag0.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag1.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag2.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag3.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_se_est_joint_diag4.png}
	\end{subfigure}
	\\
	\begin{flushleft}
		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given. The bottom panel estimates the parameters of expectation formation and inflation process jointly. From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively. }
	\end{flushleft}
	\caption{SE of Households: Esimated Model Moments and Data Moments}
\end{figure}

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Estimation of NI  for Households}
		\label{NI_diag_SCE}
		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag0.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag1.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag2.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag3.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_diag4.png}
	\end{subfigure}
	\vspace{1em}
	\vfill
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Joint Estimation of SE and Inflation Process}
		\label{NI_diag_joint_SCE}
		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag0.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag1.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag2.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag3.png}
		\includegraphics[width=0.19\textwidth]{figures/sce_ni_est_joint_diag4.png}
	\end{subfigure}
	\\
	\begin{flushleft}
		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given. The bottom panel estimates the parameters of expectation formation and inflation process jointly. From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$/$\overline{Var}_t$,  respectively.  }
	\end{flushleft}
	\caption{NI of Households: Esimated Model Moments and Data Moments}
\end{figure}

	\begin{sidewaystable}
	\caption{GMM Estimates of Parameters of SE and Inflation Process}
	\label{GMM_Est_SE_Table}
\begin{tabular}{llllllllllll}
	\hline 
	0        & 1  & 2    & 3   & SE: $\hat\lambda_{SPF}$(Q) & SE: $\hat\lambda_{SPF}$(Q) & SE: $\rho$ & SE: $\sigma$ & SE: $\hat\lambda_{SCE}$(M) & SE: $\hat\lambda_{SCE}$(Q) & SE: $\rho$ & SE: $\sigma$ \\
	\hline 
	Forecast &    &      &     & 0.21                       & 0.01                       & 1          & 0.1          & 1.8                        & 1                          & 1          & 0.1          \\
		\hline 
	FE       &    &      &     & 0.18                       & 0.01                       & 1          & 0.1          & 1.74                       & 1                          & 1          & 0.1          \\
		\hline 
	Forecast & FE &      &     & 0.2                        & 0.01                       & 1          & 0.1          & 1.77                       & 1                          & 1          & 0.1          \\
		\hline 
	Forecast & FE & Disg &     & 0.23                       & 0.05                       & 1          & 0.1          & 0.02                       & 0.03                       & 0.98       & 0.1          \\
		\hline 
	Forecast & FE & Disg & Var & 0.26                       & 0.05                       & 1          & 0.07         & 0.01                       & 0.03                       & 0.98       & 1.11         \\
		\hline 
\end{tabular}
\end{sidewaystable}

\begin{sidewaystable}
	\caption{GMM Estimates of Parameters of NI and Inflation Process}
	\label{GMM_Est_NI_Table}
\begin{tabular}{llllllllllllllllllll}
	0        & 1  & 2    & 3   & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & $Var$ & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$ & $Var$ & NI: $\rho$ & NI: $\sigma$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & $Var$ & NI: $\hat\sigma_{pb,SCE}$ & $\hat\sigma_{pr,SCE}$ & $Var$ & NI: $\rho$ & NI: $\sigma$ \\
	\hline 
	Forecast &    &      &     & 98.52                     & 1.69                  & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          & 98.52                     & 1.69                  & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          \\
	\hline 
	FE       &    &      &     & 151.59                    & 0.95                  & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          & 151.59                    & 0.95                  & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          \\
	\hline 
	Forecast & FE &      &     & -0.7                      & 336.37                & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          & -0.7                      & 336.37                & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          \\
	\hline 
	Forecast & FE & Disg &     & 1.63                      & 115.06                & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          & 1.63                      & 115.06                & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          \\
	\hline 
	Forecast & FE & Disg & Var & -0.63                     & 131.43                & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1          & -0.63                     & 131.43                & 0.2   & 0.5                       & 0.5                   & 0.1   & 0.8        & 0.1    \\
	\hline     
\end{tabular}
\end{sidewaystable}
